\section{Abstraction}
Self-propelled instrumentation has two major components, {\em Agent} that is a
shared library injected into an application process's address space, and {\em
  Injector} that injects {\em Agent}.
The following subsections describe the lower level components in Agent and
Injector in details.

\subsection{Agent}

\begin{itemize}
\item \textbf{Agent}. It manages the configuration and does instrumentation. An
  Agent instance is created in the init function of the {\em Agent} shared
  library.
\item \textbf{Event}. It specifies when the initial instrumentation should be
  done after the {\em Agent} shared library is loaded.  Currently, there are
  four types of Event: 1) instrumenting all callees in {\em main} function right
  away; 2) instrumenting all callees of specified functions right away; 3)
  instrumenting specified function calls right away; 4) instrumenting all
  callees in {\em main} after a given amount of time.
\item \textbf{Payload function}. It contains user-specified code.  From user's
  perspective, a payload function will be invoke before or after each function
  call in the process.  There are two types of payload functions, {\em entry
    payload} that is invoked before each function call and {\em exit payload}
  that is invoked after each function call.
\item \textbf{Point}. It represents an instrumentation point at current function
  call and is used in Payload function.
\item \textbf{Control Flow Graph (CFG) structures}. CFG structures include
  Object, Function, Block, and Edge. An Object represents a binary file (i.e.,
  an executable or a shared library), and contains a set of functions. A
  Function contains a set of Blocks. A Block is a basic block. An Edge connects
  two Blocks. Users can get related CFG structures of current function call from
  Point.
\end{itemize}

\input{section/2_dev_agent}



\subsection{Injector}
% For user / developer manual
% Two types of injection: process start and hijack

Injector is provided as a command. 
There are two types of injections.
One is to inject the {\em Agent} shared library at the very beginning of a
process.
The other is to inject the {\em Agent} in the middle of a running process.

% For developer manual
% Two types of injection: process start and hijack
\input{section/2_dev_injector}

